\section{Background} \label{sec:background}
\begin{itemize}
  \item \emph{Question: What follows the Zipf distribution? Is it the ``video
    files'' or ``video chunks''? If we change vide chunk sizes, will it
    change the popularity distribution as well? How do we account for
    it?} \\
    I think, the Zipf distribution for popularity is a very
    generic observation and probably applies to video files as well as
    to video chunks. So, I think it might not matter much if we change
    chunk sizes. Zipf distribution will still be observed on these
    different / variable sized chunks. So probably, we can go ahead
    and assume that even after chunking differently, Zipf will still
    be seen.

    \item \emph{Question: How do we take into consideration different
      video access patterns?} \\ So, as long as we don't find any
      study that talks about these patterns, we could just assign
      weights to different parts of a video and assume that that's how
      the videos are accessed. So, essentially, we also have a
      distribution of these weights. We can try various options here:
      \begin{itemize}
        \item Exponential (Initial parts watched more often than the ends)
        \item Uniform
        \item Parabolic (Not sure if the name is correct, but what I
          mean is - ends are watched more often than the middle) We
          could ignore these patterns to start off, and once we have
          got a working system we could then incorporate them.
      \end{itemize}
\end{itemize}
